A comparison of language control while switching within versus between languages in younger and older adults.

### 2023-08-22 manuscriptINSPIRE_R1_unmarked.Rmd
Update manuscriptINSPIRE_R1_unmarked.Rmd

# flag to specify if analyses are done from scratch (takes ~6 minutes)
# if set to 0, precomputed analyses are loaded from an RData file
doanalysis <- 0

>>>>

# flag to specify if analyses are done from scratch (takes ~6 minutes)
# if set to 0, precomputed analyses are loaded from an RData file
doanalysis <- 1
